# Price-My-Car Exploratory Data Analysis.

> "You can have **data** without information, but you cannot have information without **data**." --- Daniel Keys Moran

## Objectives

## Libraries

```{r}
library(dplyr) # Data Manipulation
library(ggplot2) # Data Visualization
library(tidyr) # Data Tidying and Reshaping
library(scales) # Scale Balancing
```

```{r}
# Visualization Suuport
options(scipen = 999)
```

## Data Collection

```{r}
all_cars <- readr::read_csv("all_cars.csv")
```

## Data Information

### Data Size and Structure

```{r}
dim(all_cars)

str(all_cars)
```

## Data Insights to generate

These are the following insights we are going to generate:

-   **Distribution of Number of Car Owners**

-   **Average Selling Price by Car Owners.**

-   **Distribution of Fuel Type.**

-   **Average Selling Price by Fuel Type.**

-   **Distribution of Price.**

-   **Relationship between kilometer driven and Selling Price**

### Distribution of Number of Previous Owners

```{r}
owner_dist <-  all_cars |> group_by(no_own) |> summarise(owner_count = n()) |> arrange(desc(owner_count))

# color 
colors <- colorRampPalette(c("#FFFF00", "#FF0000"))(nrow(owner_dist))

barplot(owner_dist$owner_count, names.arg = owner_dist$no_own, main = "Distribution of Number of Previous  Owners", 
        xlab = "Number of Owners", ylab = "Count",
        col = colors)
abline(h = mean(owner_dist$owner_count), lty = 3, lwd = 3)
```

### Average Selling Price by Car Owners

```{r}
owner_price <-  all_cars |> group_by(no_own) |> summarise(avg_price = mean(Selling_price)) |> arrange(desc(avg_price))

# color
colors_blyl <- colorRampPalette(c("#0000FF", "#ADD8E6"))(nrow(owner_price))
options(scipen = 999)


#plot
barplot(owner_price$avg_price, names.arg = owner_price$no_own, main = "Distribution of prices by Number of Previous  Owners", 
        xlab = "Number of Owners", ylab = "Price",
        col = colors_blyl, ylim = c(0, max(owner_price$avg_price) * 1.1))
abline(h = mean(owner_price$avg_price), lty = 3, lwd = 3)
```
